---
title: "LLM Film Preference: Regression Analysis"
subtitle: "What predicts Bradley-Terry preference scores across 8 language models?"
author: "Jonghyun Jee"
lang: en
format:
  html:
    toc: true
    toc-depth: 3
    toc-title: "Contents"
    code-fold: true
    code-summary: "Show code"
    theme: flatly
    embed-resources: true
execute:
  warning: false
  message: false
---

## Overview

This document runs mixed-effects regressions to identify what film-level
characteristics predict LLM preference strength (`lambda_z`, standardized
Bradley-Terry log-strength) throughout 8 models.

Models are nested from sparse to full:

| ID | Predictors |
|---|---|
| M1 | `set` only (baseline) |
| M2 | `+ era_f` (era control) |
| M3 | `+ log_imdb_votes` (knowledge coverage) |
| M4 | `+ imdb_rating` (quality signal) |
| M3w | `+ log_imdb_votes + log_wiki_revisions` (parallel robustness check) |

Set A (critical + popular) is the reference category throughout.

---

## Setup

```{r}
#| label: setup
library(lme4)
library(tidyverse)
library(knitr)
library(kableExtra)
library(patchwork)
library(broom)
library(sandwich)
library(lmtest)

select <- dplyr::select
filter <- dplyr::filter

DATA_PATH <- "regression_data.csv"
```

---

## Data

```{r}
#| label: load-data
df_wide <- read.csv(DATA_PATH, stringsAsFactors = FALSE)
cat(sprintf("%d films, %d columns\n", nrow(df_wide), ncol(df_wide)))
```

### Set distribution

```{r}
#| label: set-dist
df_wide |>
  count(set) |>
  mutate(pct = sprintf("%.0f%%", n / sum(n) * 100)) |>
  kable(col.names = c("Set", "n", "%")) |>
  kable_styling(bootstrap_options = "striped",
                full_width = FALSE, position = "left")
```

### English x Set (key confound)

Set C is 86% English; Set B is 15% English.

```{r}
#| label: english-set
table(set = df_wide$set, english = df_wide$english) |>
  addmargins() |>
  kable() |>
  kable_styling(bootstrap_options = "striped",
                full_width = FALSE, position = "left")
```

### IMDb votes & ratings by set

Log IMDb votes proxies training-data coverage per film.

```{r}
#| label: votes-by-set
df_wide |>
  group_by(set) |>
  summarise(
    n              = n(),
    median_votes   = median(imdb_votes),
    mean_log_votes = mean(log_imdb_votes) |> round(2),
    sd_log_votes   = sd(log_imdb_votes)   |> round(2),
    .groups = "drop"
  ) |>
  kable(caption = "IMDb vote counts by corpus set") |>
  kable_styling(bootstrap_options = "striped",
                full_width = FALSE, position = "left")
```

```{r}
#| label: imdb-by-set-anova

# Descriptive: votes and ratings by set
df_wide |>
  group_by(set) |>
  summarise(
    n             = n(),
    mean_rating   = mean(imdb_rating,    na.rm = TRUE) |> round(2),
    sd_rating     = sd(imdb_rating,      na.rm = TRUE) |> round(2),
    median_votes  = median(imdb_votes,   na.rm = TRUE),
    mean_log_votes = mean(log_imdb_votes, na.rm = TRUE) |> round(2),
    .groups = "drop"
  ) |>
  kable(caption = "IMDb ratings and votes by corpus set") |>
  kable_styling(bootstrap_options = "striped",
                full_width = FALSE, position = "left")
```

```{r}
#| label: anova-votes

# ANOVA: do sets differ in log IMDb votes?
aov_votes <- aov(log_imdb_votes ~ set, data = df_wide)
cat("=== ANOVA: log_imdb_votes ~ set ===\n")
print(summary(aov_votes))

cat("\n=== Tukey HSD post hoc ===\n")
print(TukeyHSD(aov_votes))
```

```{r}
#| label: anova-rating

# ANOVA: do sets differ significantly in IMDb rating?
aov_rating <- aov(imdb_rating ~ set, data = df_wide)
cat("=== ANOVA: IMDb rating ~ set ===\n")
print(summary(aov_rating))

# Tukey HSD post hoc
cat("\n=== Tukey HSD post hoc ===\n")
print(TukeyHSD(aov_rating))
```

```{r}
#| label: set-votes-rating-plot
#| fig-width: 10
#| fig-height: 4.5

p1 <- ggplot(df_wide, aes(x = log_imdb_votes, y = imdb_rating,
                           color = set, shape = set)) +
  geom_point(alpha = 0.65, size = 2) +
  scale_color_manual(values = c(A = "#2563EB", B = "#D97706", C = "#0D9488"),
                      name = "Set") +
  scale_shape_manual(values = c(A = 16, B = 17, C = 15), name = "Set") +
  labs(title = "IMDb votes vs rating by corpus set",
       x = "log IMDb votes", y = "IMDb rating") +
  theme_minimal(base_size = 11)

p2 <- df_wide |>
  pivot_longer(c(log_imdb_votes, imdb_rating),
               names_to = "measure", values_to = "value") |>
  mutate(measure = recode(measure,
                          log_imdb_votes = "log IMDb votes",
                          imdb_rating    = "IMDb rating")) |>
  ggplot(aes(x = set, y = value, fill = set)) +
  geom_boxplot(alpha = 0.7, outlier.size = 1) +
  scale_fill_manual(values = c(A = "#2563EB", B = "#D97706", C = "#0D9488"),
                    guide = "none") +
  facet_wrap(~ measure, scales = "free_y") +
  labs(title = "Distribution by set", x = "Corpus set", y = NULL) +
  theme_minimal(base_size = 11)

p1 + p2
```

---

## Factor setup

```{r}
#| label: factor-setup
df_wide <- df_wide |>
  mutate(
    set   = factor(set, levels = c("A", "B", "C")),
    era_f = factor(era_f,
                   levels = c("pre1960", "1960s_70s",
                              "1980s_90s", "2000s_plus")),
    english              = as.integer(english),
    log_imdb_votes_c     = as.numeric(
      scale(log_imdb_votes,     center = TRUE, scale = FALSE)),
    imdb_rating_c        = as.numeric(
      scale(imdb_rating,        center = TRUE, scale = FALSE)),
    log_wiki_revisions_c = as.numeric(
      scale(log_wiki_revisions, center = TRUE, scale = FALSE)),
    log_wiki_length_c    = as.numeric(
      scale(log_wiki_length,    center = TRUE, scale = FALSE)),
    wiki_n_languages_c   = as.numeric(
      scale(wiki_n_languages,   center = TRUE, scale = FALSE))
  )

n_wiki <- sum(!is.na(df_wide$log_wiki_revisions))
cat(sprintf(
  "Grand-mean log_imdb_votes = %.2f  |  imdb_rating = %.2f\n",
  mean(df_wide$log_imdb_votes, na.rm = TRUE),
  mean(df_wide$imdb_rating,    na.rm = TRUE)
))
```

---

## Reshape to long format

One row per film x model (200 x 8 = 1,600 rows).
Model metadata (family, tier) is defined in a single registry table and joined here.

```{r}
#| label: model-registry

# Detect lambda_z columns from the CSV automatically
lz_cols <- grep("^lam_z_", names(df_wide), value = TRUE)

# Single source of truth: column -> label, family, tier
model_registry <- tribble(
  ~col,                                   ~label,              ~family,     ~tier,
  "lam_z_claude_sonnet_4_6",              "Claude Sonnet 4.6", "Anthropic", "Large",
  "lam_z_gpt_5_4_2026_03_05",             "GPT-5.4",           "OpenAI",    "Large",
  "lam_z_mistral_large_2512",             "Mistral Large 3",     "Mistral",   "Large",
  "lam_z_qwen_plus",                      "Qwen 2.5 Plus",         "Alibaba",   "Large",
  "lam_z_claude_haiku_4_5",               "Claude Haiku 4.5",  "Anthropic", "Small",
  "lam_z_gpt_5_4_nano_2026_03_17",        "GPT-5.4 Nano",      "OpenAI",    "Small",
  "lam_z_mistral_small_3_2_24b_instruct", "Mistral Small 3.2", "Mistral",   "Small",
  "lam_z_qwen_turbo",                     "Qwen 2.5 Turbo",        "Alibaba",   "Small"
) |>
  filter(col %in% lz_cols)

missing <- setdiff(model_registry$col, lz_cols)
if (length(missing) > 0) warning("Missing columns: ", paste(missing, collapse = ", "))
```

```{r}
#| label: reshape-long
mk_vec <- function(field) setNames(model_registry[[field]], model_registry$col)

df_long <- df_wide |>
  pivot_longer(
    cols      = all_of(model_registry$col),
    names_to  = "model_col",
    values_to = "lambda_z"
  ) |>
  filter(!is.na(lambda_z)) |>
  mutate(
    model  = mk_vec("label")[model_col],
    family = factor(mk_vec("family")[model_col],
                    levels = c("Anthropic", "OpenAI", "Mistral", "Alibaba")),
    tier   = factor(mk_vec("tier")[model_col],
                    levels = c("Small", "Large"))
  )

cat(sprintf("Long format: %d rows\n", nrow(df_long)))
```

### Mean `lambda_z` by set and model

```{r}
#| label: lz-by-set
df_long |>
  group_by(model, tier, family, set) |>
  summarise(mean_lz = round(mean(lambda_z), 3), .groups = "drop") |>
  pivot_wider(names_from = set, values_from = mean_lz,
              names_prefix = "Set_") |>
  mutate(
    family = factor(family, levels = c("OpenAI", "Anthropic", "Mistral", "Alibaba")),
    tier   = factor(tier,   levels = c("Large", "Small"))
  ) |>
  arrange(family, tier) |>
  select(model, family, tier, Set_A, Set_B, Set_C) |>
  kable(caption = "Mean lambda_z by set and model") |>
  kable_styling(bootstrap_options = "striped", full_width = FALSE)
```

```{r}
#| label: descriptive-stats

desc_vars <- c("lambda_z", "log_imdb_votes", "log_imdb_votes_c",
               "imdb_rating", "imdb_rating_c",
               "log_wiki_revisions", "log_wiki_revisions_c")

df_long |>
  dplyr::select(any_of(desc_vars)) |>
  pivot_longer(everything(),
               names_to  = "Variable",
               values_to = "value") |>
  group_by(Variable) |>
  summarise(
    N    = sum(!is.na(value)),
    Mean = mean(value, na.rm = TRUE) |> round(3),
    SD   = sd(value,   na.rm = TRUE) |> round(3),
    Min  = min(value,  na.rm = TRUE) |> round(3),
    Max  = max(value,  na.rm = TRUE) |> round(3),
    .groups = "drop"
  ) |>
  arrange(Variable) |>
  kable(caption = "Table A1: Descriptive statistics for regression variables") |>
  kable_styling(bootstrap_options = "striped", full_width = FALSE)
```


---

## Model fitting

All models are estimated via pooled OLS. Lambda_z is z-scored within each
model before pooling, which removes between-model variance in the outcome
by construction; a random intercept adds nothing under this standardization
and was confirmed to be near-zero (boundary singular fit) in preliminary
models. 

```{r}
#| label: fit-models

m1 <- lm(lambda_z ~ set, data = df_long)

m2 <- lm(lambda_z ~ set + era_f, data = df_long)

m3 <- lm(lambda_z ~ set + era_f + log_imdb_votes_c, data = df_long)

# M3w: adds Wikipedia revision count alongside IMDb votes
wiki_available <- sum(!is.na(df_long$log_wiki_revisions_c)) > 100

m3w <- tryCatch(
  lm(lambda_z ~ set + era_f +
       log_imdb_votes_c + log_wiki_revisions_c,
     data = df_long),
  error = function(e) {
    message("M3w failed: ", conditionMessage(e)); NULL
  }
)

# M4: full model -- IMDb coverage + quality signal
# M3w serves as a parallel robustness check.
m4 <- lm(lambda_z ~ set + era_f +
            log_imdb_votes_c + imdb_rating_c,
          data = df_long)

cat("Fitted: M1, M2, M3",
    if (!is.null(m3w)) ", M3w" else "",
    ", M4")

# Robust standard errors (HC3) for all primary models
m1_robust  <- coeftest(m1,  vcov = vcovHC(m1,  type = "HC3"))
m2_robust  <- coeftest(m2,  vcov = vcovHC(m2,  type = "HC3"))
m3_robust  <- coeftest(m3,  vcov = vcovHC(m3,  type = "HC3"))
m3w_robust <- if (!is.null(m3w))
                coeftest(m3w, vcov = vcovHC(m3w, type = "HC3")) else NULL
m4_robust  <- coeftest(m4,  vcov = vcovHC(m4,  type = "HC3"))
```

---

### M3 vs M3w: Wikipedia robustness check

```{r}
#| label: m3w-robustness
if (!is.null(m3w)) {
  cat("LRT: M3 vs M3w (does adding Wiki revisions help?)\n")
  print(anova(m3, m3w))

  extract_b <- function(ct, term) {
    df <- as.data.frame(ct)
    as.numeric(df[rownames(df) == term, "Estimate"])
  }
  b_m3  <- extract_b(m3_robust,  "setB")
  b_m3w <- extract_b(m3w_robust, "setB")
  m1_b  <- extract_b(m1_robust,  "setB")
  cat(sprintf("\nSet B coefficient (HC3): M3 = %.3f  |  M3w = %.3f\n",
              b_m3, b_m3w))
  cat(sprintf("Sign reversal holds under M3w: %s\n",
              ifelse(sign(b_m3w) != sign(m1_b), "YES", "NO")))
} else {
  cat("M3w not available (Wikipedia data missing)\n")
}
```

## Model comparison

```{r}
#| label: model-comparison
fitted_models <- list(M1 = m1, M2 = m2, M3 = m3)
if (!is.null(m3w)) fitted_models[["M3w"]] <- m3w
fitted_models[["M4"]]    <- m4

# Sequential F-tests: M1 -> M2 -> M3 -> M3w -> M4
# M3w is nested in M3 (adds one predictor: log_wiki_revisions_c)
# M4 is nested in M3 (adds one predictor: imdb_rating_c)
# Note: M3w and M4 are not nested in each other
if (!is.null(m3w)) {
  cat("=== M1 -> M2 -> M3 -> M4 (main sequence) ===\n")
  print(anova(m1, m2, m3, m4))
  cat("\n=== M3 -> M3w (wiki robustness within coverage step) ===\n")
  print(anova(m3, m3w))
} else {
  anova(m1, m2, m3, m4)
}
```

### Fit indices

```{r}
#| label: aic-table
formulas <- c(
  M1 = "set",
  M2 = "+ era_f",
  M3 = "+ log_imdb_votes",
  M4 = "+ imdb_rating",
  M3w = "+ log_wiki_revisions"
)

tibble(
  Model   = names(fitted_models),
  AIC     = map_dbl(fitted_models, AIC)    |> round(1),
  BIC     = map_dbl(fitted_models, BIC)    |> round(1),
  R2      = map_dbl(fitted_models,
                    \(m) summary(m)$r.squared |> round(3)),
  adj_R2  = map_dbl(fitted_models,
                    \(m) summary(m)$adj.r.squared |> round(3))
) |>
  kable(caption = "Model fit indices") |>
  kable_styling(bootstrap_options = "striped",
                full_width = FALSE, position = "left")
```

---

## Fixed-effect coefficients

### M1--M4 summaries with HC3 standard errors

```{r}
#| label: m1-summary
cat("=== M1 (HC3) ===\n")
print(m1_robust)
cat(sprintf("Adj. R2 = %.3f\n", summary(m1)$adj.r.squared))

cat("\n=== M2 (HC3) ===\n")
print(m2_robust)
cat(sprintf("Adj. R2 = %.3f\n", summary(m2)$adj.r.squared))

cat("\n=== M3 (HC3) ===\n")
print(m3_robust)
cat(sprintf("Adj. R2 = %.3f\n", summary(m3)$adj.r.squared))

cat("\n=== M4 (HC3) ===\n")
print(m4_robust)
cat(sprintf("Adj. R2 = %.3f\n", summary(m4)$adj.r.squared))
```

```{r}
cat("\n=== M3w (HC3) ===\n")
print(m3w_robust)
cat(sprintf("Adj. R2 = %.3f\n", summary(m4)$adj.r.squared))
```

### Key coefficients across M1-M4

```{r}
#| label: coef-table
tidy_robust <- function(ct, model_id) {
  m   <- unclass(ct)                      
  rn  <- rownames(m)
  tibble::tibble(
    model_id  = model_id,
    term      = rn,
    estimate  = as.numeric(m[, "Estimate"]),
    std.error = as.numeric(m[, "Std. Error"]),
    statistic = as.numeric(m[, "t value"]),
    p.value   = as.numeric(m[, "Pr(>|t|)"]),
    conf.low  = as.numeric(m[, "Estimate"]) - 1.96 * as.numeric(m[, "Std. Error"]),
    conf.high = as.numeric(m[, "Estimate"]) + 1.96 * as.numeric(m[, "Std. Error"])
  )
}

tidy_all <- bind_rows(
  tidy_robust(m1_robust, "M1"),
  tidy_robust(m2_robust, "M2"),
  tidy_robust(m3_robust, "M3"),
  tidy_robust(m4_robust, "M4")
)

key_terms <- c("setB", "setC",
               "log_imdb_votes_c", "imdb_rating_c")

term_labels <- c(
  setB             = "Set B (critical only)",
  setC             = "Set C (commercial only)",
  log_imdb_votes_c = "log IMDb votes (centered)",
  imdb_rating_c    = "IMDb rating (centered)"
)

tidy_all |>
  filter(term %in% key_terms) |>
  mutate(
    Predictor = term_labels[term],
    sig = case_when(p.value < .001 ~ "***",
                    p.value < .01  ~ "**",
                    p.value < .05  ~ "*",
                    TRUE           ~ ""),
    across(c(estimate, std.error, conf.low, conf.high),
           \(x) round(x, 3)),
    p.value = round(p.value, 4)
  ) |>
  select(model_id, Predictor, estimate, std.error,
         conf.low, conf.high, p.value, sig) |>
  arrange(Predictor, model_id) |>
  kable(col.names = c("Model", "Predictor", "b", "SE",
                      "CI low", "CI high", "p", ""),
        caption = "Key fixed-effect coefficients") |>
  kable_styling(bootstrap_options = "striped", full_width = FALSE)
```

### Set B from M1 to M4

```{r}
#| label: attenuation
get_b <- function(robust_ct, term_name) {
  df <- as.data.frame(robust_ct)
  as.numeric(df[rownames(df) == term_name, "Estimate"])
}

m1_setB  <- get_b(m1_robust, "setB")
m4_setB  <- get_b(m4_robust, "setB")
direction <- ifelse(sign(m1_setB) != sign(m4_setB),
                    "SIGN REVERSAL", "attenuation")
change    <- m4_setB - m1_setB

cat(sprintf(
  "Set B coefficient M1 -> M4:\n  M1 (set only):  b = %.3f\n  M4 (full):      b = %.3f\n  Change:         %+.3f (%s)\n",
  m1_setB, m4_setB, change, direction
))
```

---

## Coefficient forest plot

```{r}
#| label: coef-plot
#| fig-width: 9
#| fig-height: 5.5

tidy_all |>
  filter(term %in% key_terms) |>
  mutate(term_label = factor(term_labels[term],
                             levels = rev(term_labels))) |>
  ggplot(aes(x = estimate, y = term_label,
             color = model_id, shape = model_id)) +
  geom_vline(xintercept = 0, linetype = "dashed",
             color = "grey60", linewidth = 0.6) +
  geom_errorbarh(aes(xmin = conf.low, xmax = conf.high),
                 height = 0.18, linewidth = 0.7,
                 position = position_dodge(width = 0.65)) +
  geom_point(size = 3.0,
             position = position_dodge(width = 0.65)) +
  scale_color_manual(
    values = c(M1 = "#94A3B8", M2 = "#2563EB",
               M3 = "#D97706", M4 = "#16A34A"),
    name = "Model"
  ) +
  scale_shape_manual(
    values = c(M1 = 16, M2 = 17, M3 = 15, M4 = 18),
    name = "Model"
  ) +
  labs(
    title    = "Fixed-Effect Coefficients: M1 to M4",
    subtitle = "Outcome: standardized BT score  |  95% CI  |  Set A = reference",
    x = "Coefficient estimate",
    y = NULL
  ) +
  theme_minimal(base_size = 13) +
  theme(
    axis.text = element_text(size = 13)
  )
  theme(panel.grid.major.y = element_blank(),
        legend.position = "right")
```

---

## Per-model set coefficients

```{r}
#| label: per-model-coefs
#| fig-width: 11
#| fig-height: 6

model_levels <- model_registry |>
  arrange(tier, family) |>
  pull(label)

per_model_coefs <- df_long |>
  group_by(model, tier, family) |>
  group_modify(~ {
    fit <- lm(lambda_z ~ set + era_f +
                log_imdb_votes_c + imdb_rating_c, data = .x)
    ct  <- coeftest(fit, vcov = vcovHC(fit, type = "HC3"))
    m   <- unclass(ct)
    tibble::tibble(
      term      = rownames(m),
      estimate  = as.numeric(m[, "Estimate"]),
      std.error = as.numeric(m[, "Std. Error"]),
      conf.low  = as.numeric(m[, "Estimate"]) - 1.96 * as.numeric(m[, "Std. Error"]),
      conf.high = as.numeric(m[, "Estimate"]) + 1.96 * as.numeric(m[, "Std. Error"])
    ) |> dplyr::filter(term %in% c("setB", "setC"))
  }) |>
  ungroup() |>
  mutate(
    term_label = ifelse(term == "setB",
                        "Set B (critical only)",
                        "Set C (commercial only)"),
    model = factor(model, levels = model_levels)
  )

per_model_coefs |>
  ggplot(aes(x = estimate, y = model,
             color = tier, shape = family)) +
  geom_vline(xintercept = 0, linetype = "dashed",
             color = "grey60", linewidth = 0.6) +
  geom_errorbarh(aes(xmin = conf.low, xmax = conf.high),
                 height = 0.25, linewidth = 0.7) +
  geom_point(size = 3.2) +
  facet_wrap(~ term_label, scales = "free_x") +
  scale_color_manual(
    values = c(Large = "#1E3A5F", Small = "#94A3B8"),
    name = "Tier"
  ) +
  scale_shape_manual(
    values = c(Anthropic = 16, OpenAI = 17,
               Mistral = 15, Alibaba = 18),
    name = "Family"
  ) +
  labs(
    title    = "Per-Model Set Coefficients (M4 covariates)",
    subtitle = "OLS per model  |  95% CI  |  Set A = reference",
    x = "Coefficient estimate",
    y = NULL
  ) +
  theme_minimal(base_size = 11) +
  theme(panel.grid.major.y = element_blank())
```

---

## M4 diagnostics

```{r}
#| label: diagnostics
#| fig-width: 10
#| fig-height: 8

par(mfrow = c(2, 2))

plot(fitted(m4), residuals(m4),
     xlab = "Fitted", ylab = "Residuals",
     main = "Residuals vs Fitted",
     pch = 19, cex = 0.5, col = adjustcolor("steelblue", 0.4))
abline(h = 0, lty = 2, col = "red")

qqnorm(residuals(m4), main = "Normal Q-Q",
       pch = 19, cex = 0.5, col = adjustcolor("steelblue", 0.4))
qqline(residuals(m4), col = "red")

plot(fitted(m4), sqrt(abs(residuals(m4))),
     xlab = "Fitted", ylab = "sqrt(|Residuals|)",
     main = "Scale-Location",
     pch = 19, cex = 0.5, col = adjustcolor("steelblue", 0.4))

# Mean residual by model: near-zero values confirm pooled OLS is appropriate
mean_resid <- df_long |>
  mutate(resid = residuals(m4)) |>
  group_by(model) |>
  summarise(mean_resid = mean(resid), .groups = "drop") |>
  arrange(mean_resid)

dotchart(mean_resid$mean_resid,
         labels = mean_resid$model,
         main   = "Mean Residual by Model (M4)",
         xlab   = "Mean residual (~0 confirms pooled OLS is appropriate)",
         pch    = 19, col = "steelblue")
abline(v = 0, lty = 2, col = "red")

par(mfrow = c(1, 1))
```


```{r}
#| label: rating-set-confound

# Correlation between imdb_rating and set dummies
cat("Correlation: imdb_rating x set_B =",
    round(cor(df_wide$imdb_rating, df_wide$set_B, use = "complete"), 3), "\n")
cat("Correlation: imdb_rating x set_C =",
    round(cor(df_wide$imdb_rating, df_wide$set_C, use = "complete"), 3), "\n")

# VIF: check multicollinearity in M3w and M4
library(car)

cat("VIF for M3w (IMDb votes + Wiki revisions):\n")
if (!is.null(m3w)) {
  vif_m3w <- vif(m3w)
  print(round(vif_m3w, 3))
  cat("\nNote: r(log_imdb_votes, log_wiki_revisions) = 0.93;\n")
  cat("M3w is a robustness check, not an additive theoretical step.\n")
}

cat("\nVIF for M4 (full model):\n")
# VIF for M4 -- check collinearity with both coverage proxies
vif_m4 <- vif(m4)
print(round(vif_m4, 3))

# Show M3 vs M4 set coefficients side by side
bind_rows(
  tidy_robust(m3_robust, "M3"),
  tidy_robust(m4_robust, "M4")
) |>
  filter(term %in% c("setB", "setC")) |>
  mutate(across(c(estimate, std.error, conf.low, conf.high),
                \(x) round(x, 3))) |>
  select(model_id, term, estimate, std.error, conf.low, conf.high) |>
  kable(caption = "Set B and Set C: M3 vs M4 (HC3 SEs)") |>
  kable_styling(bootstrap_options = "striped", full_width = FALSE)
```