---
title: "LLM Film Preference: Primary Analysis"
subtitle: "H2 (Critical Acclaim Orientation), H3 (Dual Legitimacy), H4 (Scale Effect)"
author: "Jonghyun Jee"
lang: en
format:
  html:
    toc: true
    toc-depth: 3
    toc-title: "Contents"
    code-fold: true
    code-summary: "Show code"
    theme: flatly
    embed-resources: true
execute:
  warning: false
  message: false
---

## Overview

Primary hypothesis tests using exact BT comparison outcomes and
per-film lambda_z estimates aggregated from 8 model result JSONs.

| Source file | Contents |
|---|---|
| `comparison_outcomes.csv` | Win counts per set-pair per model (from BT match logs) |
| `film_lambdas.csv` | Per-film lambda, lambda_z, set, rank per model |

| Hypothesis | Test | Source |
|---|---|---|
| H2 | Set B vs C win rate > 0.50 (binomial) | comparison_outcomes.csv |
| H3 | Set A win rate vs B and vs C | comparison_outcomes.csv |
| H4 | Scale effect on B vs C across tiers | comparison_outcomes.csv |
| Effect sizes | Cohen's d on lambda_z distributions | film_lambdas.csv |

---

## Setup

```{r}
#| label: setup
library(tidyverse)
library(knitr)
library(kableExtra)
library(patchwork)
library(ggplot2)

OUTCOMES_PATH <- "comparison_outcomes.csv"
LAMBDAS_PATH  <- "film_lambdas.csv"

FAMILY_LEVELS <- c("OpenAI", "Anthropic", "Mistral", "Alibaba")
TIER_LEVELS   <- c("Large", "Small")
```

---

## Load data

```{r}
#| label: load-data
outcomes <- read.csv(OUTCOMES_PATH, stringsAsFactors = FALSE) |>
  mutate(
    family = factor(family, levels = FAMILY_LEVELS),
    tier   = factor(tier,   levels = TIER_LEVELS)
  )

lambdas <- read.csv(LAMBDAS_PATH, stringsAsFactors = FALSE) |>
  mutate(
    set    = factor(set,    levels = c("A", "B", "C")),
    family = factor(family, levels = FAMILY_LEVELS),
    tier   = factor(tier,   levels = TIER_LEVELS)
  )

cat(sprintf("comparison_outcomes: %d rows x %d cols\n",
            nrow(outcomes), ncol(outcomes)))
cat(sprintf("film_lambdas:        %d rows x %d cols\n",
            nrow(lambdas), ncol(lambdas)))

# Model ordering: family then tier
model_order <- lambdas |>
  distinct(model, family, tier) |>
  arrange(tier, family) |>
  pull(model)
```

### Data check: BvC win rates match Python results

```{r}
#| label: data-check
bvc_check <- outcomes |>
  filter(set_winner == "B", set_loser == "C") |>
  arrange(tier, desc(win_rate)) |>
  mutate(win_rate_pct = sprintf("%.1f%%", win_rate * 100))

bvc_check[, c("model", "tier", "win_rate_pct", "wins", "total")] |>
  setNames(c("Model", "Tier", "Win rate", "Wins", "Total")) |>
  kable(caption = "Set B vs C win rates (from comparison_outcomes.csv)",
        row.names = FALSE) |>
  kable_styling(bootstrap_options = "striped",
                full_width = FALSE, position = "left")
```

---

## Helper functions

```{r}
#| label: helpers

# One-sided binomial test: win_rate > 0.50
run_binom <- function(wins, total) {
  bt <- binom.test(wins, total, p = 0.5, alternative = "greater")
  list(p = bt$p.value,
       sig = case_when(bt$p.value < .001 ~ "***",
                       bt$p.value < .01  ~ "**",
                       bt$p.value < .05  ~ "*",
                       TRUE              ~ "n.s."))
}

# Two-sample Cohen's d (pooled SD)
cohens_d <- function(x, y) {
  nx <- length(x); ny <- length(y)
  sp <- sqrt(((nx - 1) * var(x) + (ny - 1) * var(y)) / (nx + ny - 2))
  (mean(x) - mean(y)) / sp
}

# Significance stars
sig_stars <- function(p) {
  case_when(p < .001 ~ "***", p < .01 ~ "**",
            p < .05  ~ "*",   TRUE    ~ "n.s.")
}
```

---

## H2 -- Critical Acclaim Orientation

Set B (critically acclaimed) wins significantly more than 50% of
head-to-head matchups against Set C (commercially successful).

```{r}
#| label: h2-compute
h2 <- outcomes |>
  filter(set_winner == "B", set_loser == "C") |>
  mutate(
    p_binom = map2_dbl(wins, total,
                       \(w, n) run_binom(w, n)$p),
    sig     = map2_chr(wins, total,
                       \(w, n) run_binom(w, n)$sig)
  )

# Cohen's d from lambda_z
h2_d <- lambdas |>
  filter(set %in% c("B", "C")) |>
  group_by(model, family, tier) |>
  summarise(
    cohens_d = cohens_d(lambda_z[set == "B"],
                        lambda_z[set == "C"]),
    .groups = "drop"
  )

h2 <- h2 |>
  left_join(h2_d, by = c("model", "family", "tier")) |>
  arrange(family, tier)
```

```{r}
#| label: h2-table
h2 |>
  mutate(
    `Win rate`   = sprintf("%.1f%%", win_rate * 100),
    `Wins/Total` = sprintf("%d/%d", wins, total),
    `Cohen's d`  = sprintf("%.2f", cohens_d),
    `p (binom)`  = ifelse(p_binom < .001, "< .001",
                          sprintf("%.4f", p_binom))
  ) |>
  select(Model = model, Family = family, Tier = tier,
         `Win rate`, `Wins/Total`, `Cohen's d`, `p (binom)`, ` ` = sig) |>
  kable(caption = "H2 -- Set B vs Set C win rates (binomial test vs p = 0.50)") |>
  kable_styling(bootstrap_options = "striped", full_width = FALSE) |>
  footnote(general = "Win rates from actual BT comparison outcomes. Cohen's d from lambda_z distributions.")
```

```{r}
#| label: h2-summary-by-tier
cat("Large tier:\n")
h2 |> filter(tier == "Large") |>
  summarise(mean_wr = mean(win_rate) |> round(3),
            range   = sprintf("%.1f%%-%.1f%%",
                              min(win_rate)*100, max(win_rate)*100),
            mean_d  = mean(cohens_d) |> round(2)) |>
  print()

cat("\nSmall tier:\n")
h2 |> filter(tier == "Small") |>
  summarise(mean_wr = mean(win_rate) |> round(3),
            range   = sprintf("%.1f%%-%.1f%%",
                              min(win_rate)*100, max(win_rate)*100),
            mean_d  = mean(cohens_d) |> round(2)) |>
  print()
```

```{r}
#| label: h2-plot
#| fig-width: 9
#| fig-height: 4.5
h2 |>
  mutate(model = factor(model, levels = model_order)) |>
  ggplot(aes(x = model, y = win_rate, fill = tier)) +
  geom_col(width = 0.65, alpha = 0.85) +
  geom_hline(yintercept = 0.5, linetype = "dashed",
             colour = "grey50", linewidth = 0.7) +
  geom_text(aes(label = sprintf("%.1f%%", win_rate * 100)),
            vjust = -0.4, size = 3.5, family = "mono") +
  scale_fill_manual(values = c(Large = "#1E3A5F", Small = "#94A3B8"),
                    name = "Tier") +
  scale_y_continuous(labels = scales::percent_format(accuracy = 1),
                     limits = c(0, 1.05), expand = c(0, 0)) +
  labs(title    = "H2 -- Set B vs Set C Win Rates",
       subtitle = "All models p < .001 vs chance  |  dashed = 0.50",
       x = NULL, y = "Set B win rate") +
  theme_minimal(base_size = 11) +
  theme(axis.text.x = element_text(angle = 25, hjust = 1),
        panel.grid.major.x = element_blank())
```

---

## H3 -- Dual Legitimacy

Set A (dual-legitimacy) win rates against Set B and Set C. H3 predicts A > B.

```{r}
#| label: h3-compute
get_comparison <- function(winner, loser) {
  outcomes |>
    filter(set_winner == winner, set_loser == loser) |>
    mutate(
      p_binom = map2_dbl(wins, total,
                         \(w, n) run_binom(w, n)$p),
      sig     = map2_chr(wins, total,
                         \(w, n) run_binom(w, n)$sig)
    )
}

h3_ab <- get_comparison("A", "B")
h3_ac <- get_comparison("A", "C")

# Cohen's d for A vs B and A vs C
d_ab <- lambdas |>
  filter(set %in% c("A", "B")) |>
  group_by(model, family, tier) |>
  summarise(d_ab = cohens_d(lambda_z[set == "A"],
                            lambda_z[set == "B"]),
            .groups = "drop")

d_ac <- lambdas |>
  filter(set %in% c("A", "C")) |>
  group_by(model, family, tier) |>
  summarise(d_ac = cohens_d(lambda_z[set == "A"],
                            lambda_z[set == "C"]),
            .groups = "drop")

h3 <- h3_ab |>
  select(model, family, tier,
         AvB_rate = win_rate, AvB_wins = wins,
         AvB_total = total, AvB_p = p_binom, AvB_sig = sig) |>
  left_join(
    h3_ac |> select(model,
                    AvC_rate = win_rate, AvC_wins = wins,
                    AvC_total = total, AvC_p = p_binom, AvC_sig = sig),
    by = "model"
  ) |>
  left_join(d_ab, by = c("model", "family", "tier")) |>
  left_join(d_ac, by = c("model", "family", "tier")) |>
  arrange(family, tier)
```

```{r}
#| label: h3-table
h3 |>
  mutate(
    `A vs B` = sprintf("%.1f%% %s (d=%+.2f)",
                       AvB_rate*100, AvB_sig, d_ab),
    `A vs C` = sprintf("%.1f%% %s (d=%+.2f)",
                       AvC_rate*100, AvC_sig, d_ac)
  ) |>
  select(Model = model, Tier = tier, `A vs B`, `A vs C`) |>
  kable(
    caption = "H3 -- Set A win rates vs Set B (hypothesis) and Set C (context)"
  ) |>
  kable_styling(bootstrap_options = "striped", full_width = FALSE) |>
  footnote(general = paste(
    "Positive d = Set A preferred; negative d = Set B preferred."
  ))
```

```{r}
#| label: h3-by-tier
cat("A vs B by tier:\n")
h3 |>
  select(model, tier, AvB_rate, AvB_sig, d_ab) |>
  mutate(across(c(AvB_rate, d_ab), \(x) round(x, 3))) |>
  arrange(tier, desc(AvB_rate)) |>
  print()
```

```{r}
#| label: h3-plot
#| fig-width: 10
#| fig-height: 5
h3 |>
  pivot_longer(c(AvB_rate, AvC_rate),
               names_to = "comparison", values_to = "rate") |>
  mutate(
    comparison = recode(comparison,
                        AvB_rate = "A vs B (H3 test)",
                        AvC_rate = "A vs C (context)"),
    model = factor(model, levels = model_order)
  ) |>
  ggplot(aes(x = model, y = rate,
             fill = tier, alpha = comparison)) +
  geom_col(position = position_dodge(width = 0.7), width = 0.6) +
  geom_hline(yintercept = 0.5, linetype = "dashed",
             colour = "grey50", linewidth = 0.7) +
  scale_fill_manual(values = c(Large = "#1E3A5F", Small = "#94A3B8"),
                    name = "Tier") +
  scale_alpha_manual(values = c("A vs B (H3 test)" = 0.95,
                                "A vs C (context)" = 0.40),
                     name = "Comparison") +
  scale_y_continuous(labels = scales::percent_format(accuracy = 1),
                     limits = c(0, 1.05), expand = c(0, 0)) +
  labs(title    = "H3 -- Set A Win Rates",
       subtitle = "Solid = A vs B (H3 test)  |  Transparent = A vs C (context)  |  dashed = 0.50",
       x = NULL, y = "Set A win rate") +
  theme_minimal(base_size = 11) +
  theme(axis.text.x = element_text(angle = 25, hjust = 1),
        panel.grid.major.x = element_blank())
```

```{r}
# Model display order and title for each panel
model_titles <- model_order

lambdas_plot <- lambdas |>
  mutate(
    model    = factor(model, levels = model_order),
    set      = factor(set,   levels = c("A", "B", "C")),
    set_label = factor(set,
                       levels = c("A", "B", "C"),
                       labels = c("Set A\n(Critical + Popular)",
                                  "Set B\n(Critical Only)",
                                  "Set C\n(Popular Only)"))
  )

#| label: violin-plot
#| fig-width: 16
#| fig-height: 10

medians <- lambdas_plot |>
  group_by(model, set, set_label) |>
  summarise(med = median(lambda_z), .groups = "drop") |>
  mutate(med_label = sprintf("%+.2f", med))

set_colours <- c(A = "#5B9ABD", B = "#D4894A", C = "#4FA899")
set_fills   <- c(A = "#ADD0E8", B = "#F5CFA0", C = "#A8D8D4")

lambdas_plot <- lambdas |>
  mutate(
    model    = factor(model, levels = model_order),
    set      = factor(set, levels = c("A", "B", "C")),
    set_label = factor(set, levels = c("A", "B", "C"),
                       labels = c("Set A", "Set B", "Set C"))
  )

medians <- lambdas_plot |>
  group_by(model, set, set_label) |>
  summarise(med = median(lambda_z), .groups = "drop") |>
  mutate(med_label = sprintf("%+.2f", med))

ggplot(lambdas_plot, aes(x = set_label, y = lambda_z, fill = set)) +

  # Violin
  geom_violin(colour = NA, alpha = 0.50, trim = TRUE) +

  # IQR bar
  stat_summary(aes(colour = set),
               fun.min = \(x) quantile(x, 0.25),
               fun.max = \(x) quantile(x, 0.75),
               fun     = median,
               geom    = "linerange",
               linewidth = 2.0, alpha = 0.85) +

  # Median tick
  stat_summary(aes(colour = set),
               fun  = median,
               geom = "crossbar",
               width = 0.22, linewidth = 0.7) +

  # Individual films -- smaller, more transparent
  # geom_jitter(aes(color = set),
              #width = 0.06, size = 0.7,
              #alpha = 0.35, shape = 16) +

  # Reference line
  geom_hline(yintercept = 0, linetype = "dashed",
             colour = "grey55", linewidth = 0.4) +

  geom_text(data = medians,
            aes(x    = set_label,
                y    = -2.15,
                label = med_label,
                colour = set),
            size = 2.6, hjust = 0.5,
            fontface = "plain", family = "mono",
            inherit.aes = FALSE) +

  facet_wrap(~ model, nrow = 2, ncol = 4) +

  scale_fill_manual(
    values = set_fills,
    labels = c("Set A: Critical + Popular",
               "Set B: Critical Only",
               "Set C: Popular Only"),
    name = NULL
  ) +
  scale_colour_manual(
    values = set_colours,
    labels = c("Set A: Critical + Popular",
               "Set B: Critical Only",
               "Set C: Popular Only"),
    name = NULL
  ) +
  scale_y_continuous(
    limits = c(-2.3, 2.3),
    breaks = seq(-2, 2, 1),
    labels = c("-2", "-1", "0", "+1", "+2")
  ) +
  scale_x_discrete(labels = c("A", "B", "C")) +
  labs(
    title    = "H3 & H4: Preference Distribution by Corpus Set",
    subtitle = "Bar = IQR  |  line = median",
    x = NULL,
    y = "Standardized lambda_z"
  ) +
  theme_minimal(base_size = 10.5) +
  theme(
    strip.text         = element_text(face = "bold", size = 10.5),
    panel.grid.major.x = element_blank(),
    panel.grid.minor   = element_blank(),
    panel.spacing.x    = unit(0.8, "lines"),
    panel.spacing.y    = unit(1.0, "lines"),
    legend.position    = "bottom",
    legend.key.size    = unit(0.8, "lines"),
    legend.text        = element_text(size = 9),
    axis.text.x        = element_text(size = 9),
    axis.text.y        = element_text(size = 8),
    plot.title         = element_text(face = "bold", size = 13),
    plot.subtitle      = element_text(size = 9.5, colour = "grey40"),
    plot.margin        = margin(10, 15, 10, 10)
  )
```


---

## H4 -- Scale-Dependent Orientation

Within-family comparison: does B vs C win rate increase with scale more than A vs C?

```{r}
#| label: h4-compute
h4_base <- outcomes |>
  filter((set_winner == "B" & set_loser == "C") |
         (set_winner == "A" & set_loser == "C")) |>
  mutate(comparison = ifelse(set_winner == "B", "B vs C", "A vs C")) |>
  select(model, family, tier, comparison, win_rate)

h4_family <- h4_base |>
  group_by(family, comparison) |>
  summarise(
    large = win_rate[tier == "Large"],
    small = win_rate[tier == "Small"],
    delta = large - small,
    .groups = "drop"
  ) |>
  mutate(family = factor(family, levels = FAMILY_LEVELS))
```

```{r}
#| label: h4-table
h4_family |>
  mutate(across(c(large, small, delta),
                \(x) sprintf("%.1f%%", x * 100))) |>
  pivot_wider(names_from  = comparison,
              values_from = c(large, small, delta),
              names_glue  = "{comparison}_{.value}") |>
  select(Family = family,
         `B vs C_small`, `B vs C_large`, `B vs C_delta`,
         `A vs C_small`, `A vs C_large`, `A vs C_delta`) |>
  kable(
    col.names = c("Family",
                  "Small", "Large", "Delta (pp)",
                  "Small", "Large", "Delta (pp)"),
    caption   = "H4 -- Scale effect on B vs C and A vs C win rates"
  ) |>
  add_header_above(c(" " = 1,
                     "Critical acclaim orientation (H2)" = 3,
                     "Dual-legitimacy anchor" = 3)) |>
  kable_styling(bootstrap_options = "striped", full_width = FALSE)
```

```{r}
#| label: h4-coverage-check
cat("Coverage pattern check:\n")
cat("B vs C delta should exceed A vs C delta within each family.\n\n")

h4_family |>
  select(family, comparison, delta) |>
  pivot_wider(names_from = comparison, values_from = delta) |>
  mutate(
    BvC_exceeds_AvC = `B vs C` > `A vs C`,
    difference      = `B vs C` - `A vs C`
  ) |>
  mutate(across(c(`B vs C`, `A vs C`, difference),
                \(x) sprintf("%+.3f", x))) |>
  kable(caption = "H4 -- Differential scale effect") |>
  kable_styling(bootstrap_options = "striped",
                full_width = FALSE, position = "left") |>
  footnote(general = paste(
    "BvC_exceeds_AvC = TRUE means scale raises B vs C more than A vs C"
  ))
```

```{r}
#| label: h4-delta-plot
#| fig-width: 9
#| fig-height: 5
p_delta <- h4_family |>
  ggplot(aes(x = family, y = delta, fill = comparison)) +
  geom_col(position = position_dodge(width = 0.6),
           width = 0.5, alpha = 0.85) +
  geom_hline(yintercept = 0, linewidth = 0.5, colour = "grey40") +
  geom_text(aes(label = sprintf("%+.1f%%", delta * 100)),
            position = position_dodge(width = 0.6),
            vjust = -0.5, size = 3.5, family = "mono") +
  scale_fill_manual(
    values = c("B vs C" = "#1E3A5F", "A vs C" = "#94A3B8"),
    name   = "Comparison"
  ) +
  scale_y_continuous(labels = scales::percent_format(accuracy = 1),
                     limits = c(-0.02, 0.25)) +
  labs(title    = "H4 -- Scale Effect: Win Rate Increase (Large - Small)",
       x = NULL, y = "Delta win rate (large - small)") +
  theme_minimal(base_size = 11) +
  theme(panel.grid.major.x = element_blank())

p_delta
```

```{r}
#| label: h4-absolute-plot
#| fig-width: 11
#| fig-height: 5

# Absolute win rates with lines connecting small to large within family
p_abs <- h4_base |>
  mutate(model = factor(model, levels = model_order)) |>
  ggplot(aes(x = model, y = win_rate,
             colour = comparison, shape = tier,
             group = interaction(family, comparison))) +
  geom_line(linewidth = 0.8, alpha = 0.5) +
  geom_point(size = 4) +
  geom_hline(yintercept = 0.5, linetype = "dashed",
             colour = "grey60", linewidth = 0.5) +
  scale_colour_manual(
    values = c("B vs C" = "#1E3A5F", "A vs C" = "#94A3B8"),
    name   = "Comparison"
  ) +
  scale_shape_manual(
    values = c(Large = 16, Small = 17),
    name   = "Tier"
  ) +
  scale_y_continuous(labels = scales::percent_format(accuracy = 1),
                     limits = c(0.6, 1.0)) +
  labs(title    = "H4 -- Absolute Win Rates by Model",
       subtitle = "Lines connect small/large within each family  |  dashed = 0.50",
       x = NULL, y = "Win rate") +
  theme_minimal(base_size = 11) +
  theme(axis.text.x = element_text(angle = 25, hjust = 1),
        panel.grid.major.x = element_blank())

p_abs
```

---

## Effect sizes summary

Cohen's d for all three set comparisons across all models.

```{r}
#| label: effect-sizes-all

effect_sizes <- lambdas |>
  group_by(model, family, tier) |>
  summarise(
    d_BvC = cohens_d(lambda_z[set == "B"], lambda_z[set == "C"]),
    d_AvB = cohens_d(lambda_z[set == "A"], lambda_z[set == "B"]),
    d_AvC = cohens_d(lambda_z[set == "A"], lambda_z[set == "C"]),
    .groups = "drop"
  ) |>
  arrange(family, tier)

effect_sizes |>
  mutate(across(c(d_BvC, d_AvB, d_AvC), \(x) round(x, 2))) |>
  select(Model = model, Tier = tier, Family = family,
         `B vs C` = d_BvC, `A vs B` = d_AvB, `A vs C` = d_AvC) |>
  kable(
    caption = "Cohen's d for all set comparisons (positive = first set preferred)"
  ) |>
  kable_styling(bootstrap_options = "striped", full_width = FALSE) |>
  footnote(general = paste(
    "B vs C: positive = Set B preferred (H2).",
    "A vs B: positive = Set A preferred (H3); negative = Set B preferred.",
    "A vs C: positive = Set A preferred."
  ))
```
